---
title: "Summary of Parameters for Rpath"
author: "Sarah Gaichas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)  
library(atlantisom)
library(ggthemes)

```

## Species in Atlantis for Rpath

```{r}

```


## Total Catch

Already in mskeyrun? Yes. 

Plot it. 

```{r}
# make sure to install mskeyrun branch sarah_wgsamsim as not yet in main branch

# make a catch series function that can be split by fleet? this doesnt
# also note different time (days) from model timestep in all other output
plotC <- function(dat, truedat=NULL){
  
    ctbio <- dat %>% filter(variable=="catch")
    ctcv <- dat %>% filter(variable=="cv")
  
    ggplot() +
    geom_line(data=ctbio, aes(x=year,y=value, color="Catch biomass"), 
              alpha = 10/10) +
    {if(!is.null(truedat)) geom_line(data=truedat, aes(x=time/365,y=atoutput, color="True Catch"), alpha = 3/10)} + 
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("tons") +
    labs(colour=dat$ModSim) +
    facet_wrap(~Name, scales="free") 
  
}

catchbio_ss <- mskeyrun::simCatchIndexFW #atlantisom::read_savedfisheries(d.name, 'Catch')

plotC(catchbio_ss)
```

### Fishery catch time series
```{r catchind-1, results="asis", message=FALSE, warning=FALSE}
# observed catch only
plotC(catchbio_ss)
```


## Total Biomass

Work in progress

Avaliable for age structured fish groups

Add other age structured groups

Add biomass pools

## Diets for all

Did I pull this?

## Total Production 

Can we get total production from Atlantis? What is in PROD.nc

Or do we need to sum the catch and consumption removals with the population growth in each year to get production



## Total Consumption

Already have this from detailed diet check



